\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-22 arch.tex
updates to intro etc
Corrections from William comments and refined shopping pictures to clarify internal/external timelines

\section{Planning and execution in the \rx architecture}
\label{sec:arch}

@@

% \begin{figure}[!htbp]
%   \centering
%   \includegraphics[scale=0.35]{figs/DAG-hierarchy}
%   \caption{\small An example of a \rx reactor hierarchy which is used
%     to determine a synchronization order for propagation of values in
%     \emph{external} state variables.}
%   \label{fig:reactor-DAG}
% \end{figure}
\fcomment{I removed this figure as the next one is mucjh more
  detailed and vehiculate the same idea}

@@

One critical aspect to take into account is that from a \rx point of
view, synchronization is the only critical task of a reactor. Such a
process is used in order for the agent to identify its current state
and maintain it consistently throughout the agent's lifetime. For a
reactor not being able to find a consistent solution during
synchronization -- implying that after evaluating all possible
solutions provided by a model it was unable to find a consistent plan
-- not only indicates that a reactor is unable to explain the state of
the world, but more importantly it may jeopardize other reactors that
rely on its {\em internal} state. For this reason a failure to
synchronize immediately results in the \rx agent killing a reactor and
notifying any reactor that depends on its {\em internal} state
variables; it does so by posting the special observation
\textsf{Failed}. By so doing we allow for graceful degradation where
other reactors can readapt their plans on receipt of this observation.

@@

\subsubsection{Deliberation: Planning for future state evolution}
\label{sec:arch:plan}

@@

Consider for example the Shopping Agent model where the \texttt{Agent}
is an {\em external} timeline. As the reactor adds a goal to
\texttt{Own} milk and the current {\em external} timeline indicates
that the robot was \texttt{At(home)}, it produces a plan as shown in
Fig. \ref{fig:shop:exec0}. The {\em external} part of the plan --
namely the tokens \texttt{Going(home, superMarket)} and
\texttt{At(SuperMarket)} -- are installed as goals for the reactor
managing this state variable internally.

\begin{figure}[!htb]
  \centering
  \subfloat[\small A plan produced before synchronization.]{\label{fig:shop:exec0}\includegraphics[width=0.45\columnwidth]{figs/shoping_exec_t0}}
  \subfloat[\small Result of synchronization after the {\em Going}
  observation was received by the reactor with the plan showed in
    \ref{fig:shop:exec0}.]{\label{fig:shop:exec1}\includegraphics[width=0.48\columnwidth]{figs/shoping_exec_t1}}
    \caption{\small Shopping example: Tokens in red indicate
      observations, tokens in blue the goal that this plan attempts to
      solve for. Arrows indicate temporal constraints. }
  \label{fig:shop:exec}
\end{figure}

>>>>

\section{Planning and execution with \rx}
\label{sec:arch}

@@

% \begin{figure}[!htbp]
%   \centering
%   \includegraphics[scale=0.35]{figs/DAG-hierarchy}
%   \caption{\small An example of a \rx reactor hierarchy which is used
%     to determine a synchronization order for propagation of values in
%     \emph{external} state variables.}
%   \label{fig:reactor-DAG}
% \end{figure}
% \fcomment{I removed this figure as the next one is mucjh more
%   detailed and vehiculate the same idea}

@@

One critical aspect to take into account is that from a \rx point of
view, synchronization is the only critical task of a reactor. Such a
process is used in order for the agent to identify its current state
and maintain it consistently throughout the agent's lifetime. For a
reactor not being able to find a consistent solution during
synchronization -- implying that after evaluating all possible
solutions provided by a model it was unable to find a consistent plan
-- not only indicates that a reactor is unable to explain the state of
the world, but more importantly it may jeopardize other reactors that
rely on its {\em internal} state. For this reason a failure to
synchronize immediately results in the \rx agent killing a reactor and
notifying any reactor that depends on its {\em internal} state
variables; it does so by posting the special observation
\textsf{Failed}. This special state is a special predicate which is
acceptable for all the {\em internal} and {\em external} timelines of
a \eu reactor.  By so doing we allow for graceful degradation where
other reactors can readapt their plans on receipt of this observation.

@@

\subsubsection{Deliberation: Planning for  Evolving State}
\label{sec:arch:plan}

@@

Consider for example the Shopping Agent model where the timeline 
\texttt{Agent.position} is {\em external} while \texttt{Agent} is
implemented a an {\em internal} timeline. As the reactor adds a goal to
\texttt{Own} milk and the current {\em external} timeline indicates
that the robot was \texttt{At(home)}, it produces a plan as shown in
Fig. \ref{fig:shop:exec0}. The {\em external} part of the plan --
namely the tokens \texttt{Going(home, superMarket)} and
\texttt{At(SuperMarket)} -- are installed as goals for the reactor
managing this state variable internally.

\begin{figure}[!htb]
  \centering
  \subfloat[\small A plan produced before
  synchronization.]{\label{fig:shop:exec0}\includegraphics[width=0.7\columnwidth]{figs/shoping_exec_t0}} \\
  \subfloat[\small Result of synchronization after the {\em Going}
  observation was received by the reactor with the plan showed in
    \ref{fig:shop:exec0}.]{\label{fig:shop:exec1}\includegraphics[width=.7\columnwidth]{figs/shoping_exec_t1}}
    \caption{\small Shopping example: Tokens in red indicate
      observations, tokens in blue the goal that this plan attempts to
      solve for. Arrows indicate temporal constraints. }
  \label{fig:shop:exec}
\end{figure}
